Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-02 cordillera-cycle.tex
Add conclusions first shot.

\note{Nothing here at the moment.}

>>>>

Numerical simulations of the Cordilleran ice sheet through the last glacial
cycle presented in this study consistently produce two glaciation maxima during
MIS~4 (61.9--55.4\,\unit{kyr}) and MIS~2 (29.5--16.9\,\unit{kyr}), independently
of the choice of palaeo-temperature record used to force the model. This result
can be seen as a first-order agreement between the model and geomorphological
evidence, which has documented palaeo-glaciation corresponding to these two
stages. However, the timing of glaciation peaks highly depends on which record
is used to drive the model. The timing of the last glacial maximum is best
reproduced by the Antarctic record, and occurs too early in all simulations
that were driven by other records. The mismatch is greatest when forcing the
model with oceanic records from the Pacific Northwest, which are affected by a
weakening of the California current during the last glacial maximum.

In all simulations presented here, ice cover is limited to disjoint mountain ice
caps during most of the glacial cycle. This agrees with earlier interpretations
of the geomorphological evidence preceding last glacial maximum. However, our
simulations produce a persistent ice cover over the Skeena mountains during
the entire glacial cycle. During time periods when the Cordilleran ice sheet did
not exist, the Skeena ice cap appear to be fed by an eastwards precipitation
intrusion through a topographic window in the Coast Mountains. The ice cap act
as a nucleation centre at the onset of the last glacial maximum re-advance, and
may have contributed to the spectacular glacial erosional imprint of the Skeena
Mountains landscape.

Concerning the deglaciation phase, when most geological evidence is available,
none of the simulations presented here produce an ideal picture. The timing of
timing of the last glacial maximum and early deglaciation is generally best
reproduced by forcing the model with a palaeo-temperature record from
Antarctica. However, a Younger Dryas re-advance is best reproduced at places
where it has been documented using temperature forcing from the GRIP record.
Nonetheless, the patterns of deglaciation are consistent between different
simulations. They show a rapid deglaciation of the southern half of the ice
sheet, followed by unzipping of the Liard Lowland, and centripetal retract of
the ice margin towards the last palaeo-ice cover in the Skeena Mountains
during the early Holocene (10.9--9.5\,\unit{kyr}).

One must keep in mind, however, that these results are only accurate for our
choices of ice-sheet model (PISM), surface mass balance model (PDD), study
object (the Cordilleran ice sheet). Most importantly, our simplistic
palaeo-climate forcing does not include precipitation corrections in response
to the presence of the ice sheet, likely leading to overestimates of glacial
extent and volume. Nevertheless, our results identify the largely understudied
Skeena Mountains as a key area to understanding glacial dynamics of the
Cordilleran ice sheet, highlighting the need for further geological
investigation of this region.
